---
title: "Figure 2: Landscape plots"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.width=7, fig.height=6.69)
```

```{r}
library(here)
library(ggpubr)
source(here("src/setup.R"))
source(here("src/landscape_plots.R"))
```

## Read in data

```{r}
dat <- get_data(read_all = T, filtbins = T)
cells_to_keep <- dat$metrics %>% 
  filter(keep_cell == TRUE) %>% 
  filter(filter_gcbias == FALSE) %>% 
  filter(cell_type1 %in% c("Basal", "Luminal")) %>% 
  pull(cell_id)

gain_col <- config$clrs$gain_loss2$Gain
loss_col <- config$clrs$gain_loss2$Loss
```

Remove some bins close to centromeres which can have artifactual copy number calls due to mapping issues close to the centromere.

```{r}
cndat <- dat$cn %>% 
    as.data.table() %>%
  .[cell_id %in% cells_to_keep] %>% 
  remove_centromeres()
```

## Frequency across cell types


```{r, fig.width = 15}
plbasal <- cndat %>%
  filter(cell_type1 == "Basal") %>% 
  .[, list(
    gain = 100 * sum(state > ploidy, na.rm = TRUE) / .N,
    loss = 100 * sum(state < ploidy, na.rm = TRUE) / .N,
    n = .N
  ), by = .(chr, start, end)] %>%
  plottinglist_()

plluminal <- cndat %>%
  filter(cell_type1 == "Luminal") %>% 
  .[, list(
    gain = 100 * sum(state > ploidy, na.rm = TRUE) / .N,
    loss = 100 * sum(state < ploidy, na.rm = TRUE) / .N,
    n = .N
  ), by = .(chr, start, end)] %>%
  plottinglist_()

```

### Basal

```{r, fig.width = 10}
theme_set(theme_cowplot(font_size = 7, line_size = 0.25))
(landscape_basal <- genplot(plbasal, 
                            gain_col = gain_col,
                            loss_col = loss_col,
                            breaks = 100 * c(0, 0.005, 0.01), 
                            limits = 100 * c(0, 0.015), 
                            losslabels = c("0", "0.5", "1.0"),
                            mytitle = "Basal"))
```

### Luminal

```{r, fig.width = 10}
(landscape_luminal <- genplot(plluminal, 
                            gain_col = gain_col,
                            loss_col = loss_col,
                            breaks = 100 * c(0, 0.005, 0.01), 
                            limits = 100 * c(0, 0.015), 
                            losslabels = c("0", "0.5", "1.0"),
                            mytitle = "Luminal"))
```


## Per chromosome arm plots

### Single chromosomes

```{r}

singlearm_freq_cohort1 <- dat$arm_frequencies

symnum.args <- list(cutpoints = c( 0.00, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))
x1 <- dat$arm_frequencies %>% 
  filter(n_cells > config$cutoff)

mean_vals <- x1 %>% 
  filter(n_cells > config$cutoff) %>% 
  filter(cell_type1 %in% c("Luminal", "Basal")) %>% 
  group_by(name, chrarm, gain_loss) %>% 
  summarise(freq_event_mean = 100 * mean(freq_event),
            freq_event_median = 100 * median(freq_event)) %>% 
  ungroup() %>% 
  mutate(x = freq_event_mean, freq_event = freq_event_mean) %>% 
  filter(x > 0.1)

gbox <- x1 %>% 
  filter(n_cells > config$cutoff) %>% 
  filter(cell_type1 %in% c("Luminal", "Basal")) %>% 
  filter(name %in% mean_vals$name) %>% 
  group_by(name) %>% 
  mutate(x = mean(freq_event)) %>% 
  ungroup() %>% 
  mutate(freq_event = freq_event * 100) %>% 
  ggplot(aes(x = fct_reorder(name, x, .desc = T), y = freq_event, fill = cell_type1)) +
  geom_boxplot(outlier.size = 0.1, alpha = 0.7, size = 0.05, width = 0.5, outlier.colour = NA) +
  geom_point(position = position_jitterdodge(jitter.width = 0.05, jitter.height = 0.0, dodge.width = 0.5), size = 0.07) +
  scale_fill_manual(values = unlist(config$clrs$cell_type)) +
  scale_color_manual(values = "firebrick4") +
  stat_compare_means(label.y.npc = 0.9, method = "wilcox.test",
    aes(label = paste0(..p.signif..)), size = 3, symnum.args = symnum.args,
  ) +
  ylab("% cells aneuploid") +
  xlab("") +
  scale_x_discrete(guide = guide_axis(angle = 90)) +
  scale_y_continuous(trans = scales::pseudo_log_trans(sigma = 0.05, base = 10),  breaks = c(0, 1, 5, 0.1, 0.3), limits = c(0, 10)) +
  labs(fill = "") +
  theme(legend.position = "none")
gbox
```

### Pairs of chromosomes

```{r}
dat$multiarm_frequencies$sample %>% unique %>% length

dat$multiarm_frequencies[name == "1qgain_16qloss" & freq_event > 0] %>% pull(sample) %>% unique %>% length

dat$multiarm_frequencies[name == "1qgain_10qloss" & freq_event > 0] %>% pull(sample) %>% unique %>% length

x <- dat$multiarm_frequencies %>% 
  filter(cell_type1 %in% c("Luminal", "Basal")) %>% 
  filter(n_cells > config$cutoff) %>% 
  arrange(desc(freq_event)) %>% 
  group_by(name) %>% 
  summarise(n_patients = sum(n_event > 1),
            freq_event = 100 * mean(freq_event),
            total_patients = n()/2) %>% 
  ungroup() %>% 
  arrange(desc(n_patients)) %>% 
  head(20) %>% 
  filter(n_patients > 4) %>% 
  mutate(idx = 1:n()) %>% 
  select(name, idx, n_patients, total_patients)

gboxmulti <- dat$multiarm_frequencies %>% 
  filter(cell_type1 %in% c("Luminal", "Basal")) %>% 
  filter(n_cells > config$cutoff) %>% 
  arrange(desc(freq_event)) %>% 
  filter(name %in% x$name) %>% 
  group_by(name) %>% 
  mutate(x = mean(freq_event)) %>% 
  ungroup() %>% 
  mutate(name = str_replace(name, "_", "\n")) %>% 
  mutate(freq_event = freq_event * 100) %>% 
  ggplot(aes(x = fct_reorder(name, x, .desc = T), y = freq_event, fill = cell_type1)) +
  geom_boxplot(outlier.size = 0.1, alpha = 0.7, size = 0.05, width = 0.5, outlier.colour = NA) +
  #geom_point(data = mean_vals, aes(fill = NULL, col = "x"), shape = 4, size = 2.5, show.legend = FALSE) +
  geom_point(position = position_jitterdodge(jitter.width = 0.05, jitter.height = 0.0, dodge.width = 0.5), size = 0.07) +
  scale_fill_manual(values = unlist(config$clrs$cell_type)) +
  scale_color_manual(values = "firebrick4") +
  stat_compare_means(label.y.npc = 0.9, method = "wilcox.test",
    aes(label = paste0(..p.signif..)), size = 3, symnum.args = symnum.args,
  ) +
  ylab("% cells aneuploid") +
  xlab("") +
  scale_x_discrete(guide = guide_axis(angle = 90)) +
  scale_y_continuous(trans = scales::pseudo_log_trans(sigma = 0.05, base = 10),  breaks = c(0, 0.1, 0.3, 1.0), limits = 
c(0, 3)) +
  labs(fill = "") +
  theme(legend.position = "none")

gboxmulti
```

```{r}
dat$multiarm_frequencies %>% 
  filter(cell_type1 %in% c("Luminal", "Basal")) %>% 
  filter(n_cells > config$cutoff) %>% 
  arrange(desc(freq_event)) %>% 
  filter(name %in% x$name) %>% 
  group_by(name) %>% 
  mutate(x = mean(freq_event)) %>% 
  ungroup() %>% 
  mutate(name = str_replace(name, "_", "\n")) %>% 
  mutate(freq_event = freq_event * 100) %>% 
  group_by(name, cell_type1) %>% 
  summarize(f = mean(freq_event))

```

### Chromosome pairs heatmap


```{r}
multi_arm <- dat$multiarm_frequencies %>% 
  filter(cell_type1 %in% c("Luminal", "Basal")) %>% 
  mutate(event1 = paste0(chrarm1, gain_loss1),
         event2 = paste0(chrarm2, gain_loss2)) %>% 
  filter(event1 %in% mean_vals$name & event2 %in% mean_vals$name) %>% 
  filter(!(str_detect(event1, "X") | str_detect(event2, "X"))) %>% 
  group_by(event1, event2) %>% 
  summarise(freq_event = mean(freq_event),
            n_cells = sum(n_cells),
            n_event = sum(n_event)) %>% 
  ungroup() %>% 
  arrange(desc(freq_event))

mean_vals <- x1 %>% 
  filter(n_cells > config$cutoff) %>% 
  filter(cell_type1 %in% c("Luminal", "Basal")) %>% 
  #filter(cell_type == "Luminal") %>% 
  #filter(name %in% names_to_keep) %>% 
  group_by(name, chrarm, gain_loss) %>% 
  summarise(freq_event_mean = 100 * mean(freq_event),
            freq_event_median = 100 * median(freq_event)) %>% 
  ungroup() %>% 
  # pivot_wider(names_from = "gain_loss", values_from = c("freq_event_mean", "freq_event_median")) %>% 
  mutate(x = freq_event_mean, freq_event = freq_event_mean) %>% 
  filter(x > 0.1) %>% 
  arrange(desc(x)) %>% 
  select(name, x) %>% 
  filter(!str_detect(name, "X"))

mat <- matrix(nrow = 7, ncol = 7)
row.names(mat) <-  mean_vals$name
colnames(mat) <- mean_vals$name
df <- data.frame()
i <- 2
for (e1 in mean_vals$name){
  print("1")
  print(e1)
  if (i > 7){
    next
  }
  for (e2 in mean_vals$name[i:7]){
    print("2")
    print(e2)
    if (e1 == e2){
      next
    }
    x <- filter(multi_arm, event1 == e1 & event2 == e2)
    if (nrow(x) == 0){
      x <- 0
    } else{
      x <- x$freq_event
    }
    df <- bind_rows(df, data.frame(event1 = e1, event2 = e2, freq_event = x * 100))
    mat[e1, e2] <-  x * 100
  }
  i <- i + 1
}

mat_df <- reshape2::melt(as.matrix(mat), na.rm = TRUE) # Convert to long format, removing NAs
x_levels_reversed <- levels(factor(mat_df$Var1))[length(levels(factor(mat_df$Var1))):1]
y_levels_reversed <- levels(factor(mat_df$Var2))[length(levels(factor(mat_df$Var2))):1]


hmap <- ggplot(mat_df, 
       aes(x=Var1,
           y=Var2, fill=value)) +
  geom_tile(alpha = 0.5, colour = "black") +
  scale_fill_gradient(low = "white", high = "red") + # Change colors as needed
  theme_minimal(base_size = 7) +
  #scale_x_discrete(limits = x_levels_reversed) +
  scale_y_discrete(limits = y_levels_reversed) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + # Rotate x labels if needed
  scale_fill_distiller(palette = "RdBu") +
  labs(x = "Event 1", y = "Event 2", fill = "Frequency") + # Customize labels +
  theme(legend.key.width = unit(0.2, "cm"),
        legend.key.height = unit(0.3, "cm"),
        legend.position = c(0.8, 0.8)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  # theme(legend.key.width = unit(0.3, "cm"),
  #     legend.key.height = unit(0.2, "cm"),
  #     legend.position = "top") +
  labs(fill = "")
hmap
```

```{r}
dat$multiarm_frequencies %>% 
  filter(cell_type1 %in% c("Luminal", "Basal")) %>% 
  filter(n_cells > config$cutoff) %>% 
  arrange(desc(freq_event)) %>% 
  group_by(name, cell_type1) %>% 
  summarise(n_patients = sum(n_event > 0),
            freq_event = 100 * mean(freq_event),
            total_patients = n()) %>% 
  ungroup() %>% 
  arrange(desc(n_patients)) %>% 
  pivot_wider(names_from = cell_type1, values_from = c(freq_event, n_patients, total_patients)) %>% 
  arrange(desc(freq_event_Luminal)) %>% head(20)
```



### t.test multi chromosome

```{r}
library(broom)
dat$multiarm_frequencies %>% 
  filter(cell_type1 %in% c("Luminal", "Basal")) %>% 
  filter(n_cells > config$cutoff) %>% 
  arrange(desc(freq_event)) %>% 
  mutate(freq_event = freq_event * 100) %>% 
  group_by(name) %>%
  do(tidy(t.test(100 * freq_event ~ cell_type1, data = .))) %>%
  select(name, estimate,estimate1, estimate2, statistic, p.value, conf.low, conf.high) %>% 
  arrange(p.value) %>% 
  filter(!is.na(p.value)) %>% 
  DT::datatable()

```

### Wilcox.test multi chromosome

```{r}
dat$multiarm_frequencies %>% 
  filter(cell_type1 %in% c("Luminal", "Basal")) %>% 
  filter(n_cells > config$cutoff) %>% 
  arrange(desc(freq_event)) %>% 
  mutate(freq_event = freq_event * 100) %>% 
  group_by(name) %>%
  do(tidy(wilcox.test(100 * freq_event ~ cell_type1, data = .))) %>%
  select(name, statistic, p.value) %>% 
  arrange(p.value) %>% 
  filter(!is.na(p.value)) %>% 
  DT::datatable()

```


## Frequency plots for Cancer and scWGS


```{r}
cancer <- fread(paste0(config$cancerdir, "nikzainal_bins.csv.gz")) %>% 
  remove_centromeres()

htert_cells <- fread(here("../zenododirectory/htert/cn.csv.gz")) %>% 
  remove_centromeres()

pl <- cndat %>%
  .[, list(
    gain = 100 * sum(state > ploidy, na.rm = TRUE) / .N,
    loss = 100 * sum(state < ploidy, na.rm = TRUE) / .N,
    n = .N
  ), by = .(chr, start, end)] %>%
  plottinglist_() 

pl_htertcells <- htert_cells %>%
  .[, list(
    gain = 100 * sum(state > ploidy, na.rm = TRUE) / .N,
    loss = 100 * sum(state < ploidy, na.rm = TRUE) / .N,
    n = .N
  ), by = .(chr, start, end)] %>%
  plottinglist_() 

pl_cancer <- cancer %>%
  group_by(sample) %>% 
  mutate(ploidy = signals:::Mode(state)) %>% 
  ungroup() %>% 
  as.data.table() %>%
  .[, list(gain = 100 * sum(state > ploidy, na.rm = TRUE) / .N,
         loss = 100 * sum(state < ploidy, na.rm = TRUE) / .N,
         n = .N), by = .(chr, start, end)] %>%
  plottinglist_()

landscape_htertcells <- genplot(pl_htertcells,  
                                alphaval = 0.6,
                            gain_col = gain_col,
                            loss_col = loss_col,
                            breaks = 100 * c(0, 0.01), 
                            limits = 100 * c(0, 0.018), 
                            losslabels = c("0", "1.0"), 
                            mytitle = NULL, returnlist = T)

landscape_cancer <- genplot(pl_cancer, alphaval = 0.6,
                            gain_col = gain_col,
                            loss_col = loss_col,
                            breaks = 100 * c(0, 0.5), 
                            limits = 100 * c(0, 0.75), 
                            losslabels = c("0", "50"), 
                            mytitle = NULL, returnlist = T)

landscape_basal <- genplot(plbasal, 
                            gain_col = gain_col,
                            loss_col = loss_col,
                            breaks = 100 * c(0, 0.005, 0.01, 0.015), 
                            limits = 100 * c(0, 0.015), 
                            losslabels = c("0", "0.5", "1.0", "1.5"),
                            mytitle = NULL, returnlist = T)

landscape_luminal <- genplot(plluminal, 
                            gain_col = gain_col,
                            loss_col = loss_col,
                            breaks = 100 * c(0, 0.005, 0.01, 0.015), 
                            limits = 100 * c(0, 0.015), 
                            losslabels = c("0", "0.5", "1.0", "1.5"),
                            mytitle = NULL, returnlist = T)
```

## Final figure

```{r}
myplot <- cowplot::plot_grid(
  landscape_htertcells$gain + theme(legend.position = "none",
                                    axis.line = element_line(size = 0.18)) + removexaxis + ylab("hTERT\nCells"),
  landscape_cancer$gain + theme(legend.position = "none",
                                axis.line = element_line(size = 0.18)) + removexaxis + ylab("Breast\nCancers"), 
  landscape_basal$gain + theme(legend.position = "none",
                               axis.line = element_line(size = 0.18)) + removexaxis + ylab("Basal\nCells"),
  landscape_luminal$gain + theme(legend.position = "none",
                                 axis.line = element_line(size = 0.18))  + ylab("Luminal\nCells"),
  landscape_luminal$loss + theme(legend.position = "none",
                                 axis.line = element_line(size = 0.18)) + ylab("Luminal\nCells"),
  landscape_basal$loss + theme(legend.position = "none",
                               axis.line = element_line(size = 0.18)) + removexaxis + ylab("Basal\nCells"),
  landscape_cancer$loss + theme(legend.position = "none",
                                axis.line = element_line(size = 0.18))  + removexaxis + ylab("Breast\nCancers"), 
  landscape_htertcells$loss + theme(legend.position = "none",
                                    axis.line = element_line(size = 0.18))  + removexaxis + ylab("hTERT\nCells"), 
  align = "v", 
  axis = "lr", 
  ncol = 1, 
  rel_heights = c(1, 1,1,1.2, 1, 1, 1, 1))

myplot <- cowplot::plot_grid(NULL, myplot, rel_widths = c(0.05, 1))

gbottom <- cowplot::plot_grid(gbox, 
                      hmap,
                      gboxmulti, 
                      ncol = 3,
                      rel_widths = c(2,2,1), 
                      labels = c("b", "c", "d"),
                      label_size = 8)

myplot_final <- cowplot::plot_grid(myplot, NULL, gbottom, ncol = 1, rel_heights = c(4,0.18, 1.5), 
                          labels = c("a"), label_size = 8)

myplot_final %>% 
    cowplot::save_plot(here("Figures/Main/fig2.pdf"), .,base_width = 2 * 89 * 0.039, base_height = 6)
```

```{r, fig.width=7, fig.height=6}
myplot_final
```

## Correlation with TCGA

```{r, fig.height = 2.5}
tcga <- fread(paste0(config$cancerdir, "tcga_bins.csv.gz")) %>%
  mutate(chr = paste0(chr)) %>% 
  remove_centromeres()
tcga_meta <- fread(paste0(config$cancerdir, "tcga_metadata.csv.gz")) %>% 
  filter(purity > 0.5) %>% 
  select(sample, cancer_type)

tcga <- inner_join(tcga, tcga_meta)

cutoff <- 0.5
pl_tcga <- tcga %>%
  as.data.table() %>%
  .[, list(Gain = sum(copy_old > cutoff, na.rm = TRUE) / .N,
         Loss = sum(copy_old < -cutoff, na.rm = TRUE) / .N,
         n = .N), by = .(chr, start, end, cancer_type)] %>%
  plottinglist_()

#library for cosine similarity
library(lsa)

cancer_type_cor <- inner_join(plluminal$CNbins, pl_tcga$CNbins, by = c("chr", "start", "end"),suffix - c(".scwgs", ".tcga")) %>% 
  group_by(cancer_type) %>% 
  summarise(cor_gain = cor(gain, Gain),
            cor_loss = cor(loss, Loss),
            corsp_gain = cor(gain, Gain, method = "spearman"),
            corsp_loss = cor(loss, Loss, method = "spearman"),
            cosine_gain = cosine(gain, Gain)[1],
            cosine_loss = cosine(loss, Loss)[1]) %>% 
  ungroup()

htert_cor <-inner_join(plluminal$CNbins, pl_htertcells$CNbins %>% rename(Gain = gain , Loss = loss), 
           by = c("chr", "start", "end"),suffix - c(".scwgs", ".tcga")) %>%   na.omit() %>% 
  summarise(cor_gain = cor(gain, Gain),
            cor_loss = cor(loss, Loss),
            corsp_gain = cor(gain, Gain, method = "spearman"),
            corsp_loss = cor(loss, Loss, method = "spearman"),
            cosine_gain = cosine(gain, Gain)[1],
            cosine_loss = cosine(loss, Loss)[1]) %>% 
  ungroup() %>% 
  mutate(cancer_type = "hTERT")

cancer_type_cor <- bind_rows(cancer_type_cor, htert_cor) %>% 
  filter(cancer_type != "hTERT") %>%
  pivot_longer(-cancer_type) %>% 
  arrange(name, desc(value)) %>% 
  mutate(idx = 1:n()) %>% 
  filter(!is.na(cancer_type))

ggain <- cancer_type_cor %>% 
  filter(name == "cosine_gain") %>% 
  ggplot(aes(x = fct_reorder(cancer_type, idx, .desc = F), y = value)) +
  geom_col(fill = config$clrs$gain_loss2$Gain) +
  xlab("") +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  ylab("Cosine similarity - gains") +
  scale_y_continuous(limits = c(0, 1.0))
ggain

gloss <- cancer_type_cor %>% 
  filter(name == "cosine_loss") %>% 
  ggplot(aes(x = fct_reorder(cancer_type, idx, .desc = F), y = value)) +
  geom_col(fill = config$clrs$gain_loss2$Loss) +
  xlab("") +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  ylab("Cosine similarity - losses") +
  scale_y_continuous(limits = c(0, 1.0))
gloss

ggain_cor <- cancer_type_cor %>% 
  filter(name == "cor_gain") %>% 
  ggplot(aes(x = fct_reorder(cancer_type, idx, .desc = F), y = value)) +
  geom_col(fill = config$clrs$gain_loss2$Gain) +
  xlab("") +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  ylab("Correlation - gains") +
  scale_y_continuous(limits = c(NA, 1.0))
ggain_cor

gloss_cor <- cancer_type_cor %>% 
  filter(name == "cor_loss") %>% 
  ggplot(aes(x = fct_reorder(cancer_type, idx, .desc = F), y = value)) +
  geom_col(fill = config$clrs$gain_loss2$Loss) +
  xlab("") +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  ylab("Correlation - losses") +
  scale_y_continuous(limits = c(NA, 1.0))
gloss_cor


```

## Bootstrapping

```{r}
bootstrap_tcga <- function(nsamples = 10){
  tcga_ids <- tcga %>% distinct(cancer_type, sample)
  cnbins_sample <- data.frame()
  for (i in 1:nsamples){
    print(i)
    tcga_ids_sample <- tcga_ids %>% 
      slice_sample(prop = 0.75, by = "cancer_type")
    pl_tcga <- tcga %>%
      filter(sample %in% tcga_ids_sample$sample) %>% 
      as.data.table() %>%
      .[, list(Gain = sum(copy_old > cutoff, na.rm = TRUE) / .N,
             Loss = sum(copy_old < -cutoff, na.rm = TRUE) / .N,
             n = .N), by = .(chr, start, end, cancer_type)] %>%
      plottinglist_()
    cnbins_sample <- bind_rows(cnbins_sample, pl_tcga$CNbins %>% mutate(sample_idx_tcga = i))
  }
  return(cnbins_sample)
}

bootstrap_dlp <- function(nsamples = 25){
  cell_ids <- cndat %>%
    filter(cell_type1 == "Luminal") %>% distinct(cell_id)
  cnbins_sample <- data.frame()
  for (i in 1:nsamples){
    print(i)
    cell_ids_sample <- cell_ids %>% 
      slice_sample(prop = 0.75)
    plluminal <- cndat %>%
      filter(cell_id %in% cell_ids_sample$cell_id) %>% 
      .[, list(
        gain = 100 * sum(state > ploidy, na.rm = TRUE) / .N,
        loss = 100 * sum(state < ploidy, na.rm = TRUE) / .N,
        n = .N
      ), by = .(chr, start, end)] %>%
      plottinglist_()
    cnbins_sample <- bind_rows(cnbins_sample, plluminal$CNbins %>% mutate(sample_idx_dlp = i))
  }
  return(cnbins_sample)
}

cnbins_tcga <- bootstrap_tcga(nsamples = 25)
cnbins_dlp <- bootstrap_dlp(nsamples = 25)

cancer_type_cor <- inner_join(cnbins_dlp, cnbins_tcga, 
                              by = c("chr", "start", "end"),suffix - c(".scwgs", ".tcga")) %>% 
  group_by(cancer_type, sample_idx_tcga, sample_idx_dlp) %>% 
  summarise(cor_gain = cor(gain, Gain),
            cor_loss = cor(loss, Loss),
            corsp_gain = cor(gain, Gain, method = "spearman"),
            corsp_loss = cor(loss, Loss, method = "spearman"),
            cosine_gain = cosine(gain, Gain)[1],
            cosine_loss = cosine(loss, Loss)[1]) %>% 
  ungroup()

cancer_type_cor <- cancer_type_cor %>%
  pivot_longer(-cancer_type) %>% 
  arrange(name, desc(value)) %>% 
  mutate(idx = 1:n()) %>% 
  filter(!is.na(cancer_type))


theme_set(theme_cowplot(font_size = 7, line_size = 0.25))

ggain_bs <- cancer_type_cor %>% 
  filter(name == "cosine_gain") %>% 
  group_by(cancer_type) %>% 
  mutate(ord = mean(value)) %>% 
  ungroup() %>% 
  ggplot(aes(x = fct_reorder(cancer_type, ord, .desc = T), y = value)) +
  geom_violin(scale = "width",
              fill = config$clrs$gain_loss2$Gain,
              col = config$clrs$gain_loss2$Gain) +
  geom_boxplot(col = "white", 
               size = 0.2, width = 0.3, alpha = 0.5, outlier.colour = NA) +
  xlab("") +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  ylab("Cosine similarity - gains") +
  scale_y_continuous(limits = c(0, 1.0))
ggain_bs

gloss_bs <- cancer_type_cor %>% 
  filter(name == "cosine_loss") %>% 
  group_by(cancer_type) %>% 
  mutate(ord = mean(value)) %>% 
  ungroup() %>% 
  ggplot(aes(x = fct_reorder(cancer_type, ord, .desc = T), y = value)) +
  geom_violin(scale = "width",
              fill = config$clrs$gain_loss2$Loss,
              col = config$clrs$gain_loss2$Loss) +
  geom_boxplot(col = "white", 
               size = 0.2, width = 0.3, alpha = 0.5, outlier.colour = NA) +
  xlab("") +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  ylab("Cosine similarity - losses") +
  scale_y_continuous(limits = c(0, 1.0))
gloss_bs

cowplot::plot_grid(cowplot::plot_grid(NULL, NULL, ncol = 1, labels = c("a", "b"),label_size = 8),
          cowplot::plot_grid(ggain_bs, gloss_bs, ncol = 1),
          ncol = 2, rel_widths = c(0.02, 1)) %>% 
  cowplot::save_plot(.,
            filename = here("Figures/Extended/EDF3.pdf"),
            base_height = 3.4,
            base_width = 2 * 89 * 0.039)
```


## session info

```{r}
sessionInfo()
```